This is an example of article title

### 2023-07-08 paper/paper.tex
chore: Additions to paper

\section{The need for space partitioning algorithms}
Space partitioning algorithms play a pivotal role in improving the runtime
performance of computational algorithms by dividing data into smaller,
manageable sections. These algorithms are designed to optimize the performance
of computational algorithms by efficiently partitioning the data space in a
manner that aligns with the specific requirements of the problem domain.
\\\\
In this section, we delve into the need for specific space partitioning
algorithms and their significance in addressing the computational bottlenecks
faced by certain algorithms. We examine three prominent application domains:
k-nearest neighbors (kNN) search, collision detection, and the fast multipole
method (FMM). These domains represent scenarios where the all-vs-all model,
involving computations between every pair of data points, hampers the runtime
performance of algorithms.

@@

\subsection{Collision Detection}
Collision detection algorithms also stand to benefit from specific space
partitioning techniques. In scenarios where it is necessary to determine if a
collision occurs between objects in a three-dimensional space, the all-vs-all
model becomes impractical for large-scale simulations. By partitioning the
space into smaller regions or bins, collision detection algorithms can focus
computations solely on objects within the same partition. This significantly
reduces the number of pairwise collision checks required and provides a
substantial performance improvement in terms of runtime. Specific space
partitioning algorithms enable efficient identification of potential collision
candidates, contributing to faster and more accurate collision detection in
simulations and virtual environments.

>>>>

\section{Motivation}
Space partitioning algorithms play a pivotal role in improving the runtime
performance of computational algorithms by dividing data into smaller,
manageable sections. These algorithms are designed to optimize the performance
of computational algorithms by efficiently partitioning the data space in a
manner that aligns with the specific requirements of the problem domain.
\\\\
In this section, we delve into the need for space partitioning
algorithms and their significance in addressing the computational bottlenecks
faced by certain algorithms. We examine three prominent application domains:
k-nearest neighbors (kNN) search, collision detection, and the fast multipole
method (FMM). These domains represent scenarios where the all-vs-all model,
involving computations between every pair of data points, hampers the runtime
performance of algorithms.

@@

\subsection{Collision Detection}
Collision detection algorithms also stand to benefit from space
partitioning techniques. In scenarios where it is necessary to determine if a
collision occurs between objects in a $d$-dimensional space, the all-vs-all
model becomes impractical for large-scale simulations. By partitioning the
space into smaller regions or bins, collision detection algorithms can focus
computations solely on objects within the same partition. This significantly
reduces the number of pairwise collision checks required and provides a
substantial performance improvement in terms of runtime. Specific space
partitioning algorithms enable efficient identification of potential collision
candidates, contributing to faster and more accurate collision detection in
simulations and virtual environments.
